---
title: "p8105_hw1_wq2160"
author: "Wenshan Qu (wq2160)"
date: "9/28/2021"
output:
  github_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
```


## Create a data frame hw1_df comprised of: 1). a random sample of size 10 from a standard Normal distribution; 2). a logical vector indicating whether elements of the sample are greater than 0; 3). a character vector of length 10; 4). a factor vector of length 10, with 3 different factor “levels”.

```{r}
## create the data frame "hw1_df"
hw1_df =
  tibble(
    sample = rnorm(10),
    gr_than_0 = sample > 0,
    vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    vec_factor = factor(c(1, 1, 2, 3, 3, 3, 2, 3, 1, 3), 
                        levels = c("1", "2", "3"))
  )

## show the data frame
hw1_df
```


## Take the mean of each variable:

```{r, warning = false}
## take the mean of "sample"
hw1_df %>% pull(sample) %>% mean()
mean(hw1_df$sample)

## take the mean of logical vector
hw1_df %>% pull(gr_than_0) %>% mean()
mean(hw1_df$gr_than_0)

## take the mean of character vector
hw1_df %>% pull(vec_char) %>% mean()
mean(hw1_df$vec_char)

## take the mean of factor vector
hw1_df %>% pull(vec_factor) %>% mean()
mean(hw1_df$vec_factor)
```

## The result above shows that the variable "sample" and "logical factor" could be taken the mean, while the "character factor" and "factor vector" could not.

