---
title: "p8105_hw1_wq2160"
author: "Wenshan Qu (wq2160)"
date: "9/28/2021"
output:
  github_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
```

### Problem 1

#### Create a data frame hw1_df comprised of: 1). a random sample of size 10 from a standard Normal distribution; 2). a logical vector indicating whether elements of the sample are greater than 0; 3). a character vector of length 10; 4). a factor vector of length 10, with 3 different factor “levels”.

```{r}
## create the data frame "hw1_df"
hw1_df =
  tibble(
    sample = rnorm(10),
    gr_than_0 = sample > 0,
    vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    vec_factor = factor(c(1, 1, 2, 3, 3, 3, 2, 3, 1, 3), 
                        levels = c("1", "2", "3"))
  )

## show the data frame
hw1_df
```


#### Take the mean of each variable:

```{r message = FALSE, warning = FALSE, collapse = TRUE}
## take the mean of sample
hw1_df %>% pull(sample) %>% mean()
mean(hw1_df$sample)

## take the mean of logical vector
hw1_df %>% pull(gr_than_0) %>% mean()
mean(hw1_df$gr_than_0)

## take the mean of character vector
hw1_df %>% pull(vec_char) %>% mean()
mean(hw1_df$vec_char)

## take the mean of factor vector
hw1_df %>% pull(vec_factor) %>% mean()
mean(hw1_df$vec_factor)
```

#### The result above shows that the variable "sample" and "logical factor" could be taken the mean, while the "character factor" and "factor vector" could not.


#### Then, we convert the type of variables:

```{r eval = FALSE}

as.numeric(hw1_df$sample)

as.numeric(hw1_df$gr_than_0)

as.numeric(hw1_df$vec_char)

as.numeric(hw1_df$vec_factor)
```

#### The variable type of "sample" and "logical vector" could be converted, the "character factor" could not be converted because it is nominal data. As for "factor vector", I defined it as numeric factor so it could be converted to numbers here; but if I denined it as "male", "female", and "prefer not to say", then it could NOT be converted and the output will be "NA".

#### Another thing about the "factor vector" is that: Why the mean of vec_factor could not be calculated but it could be converted to numbers. My explanition is: in the data frame, I defined vec_factor using `c()`, so even the factors are actually numbers, they are not considered as numbers by R (they are considered more like "text"). But because they are really numbers, they could be converted to numbers using `as.numeric` function. 


### Problem 2
```{r}
## load "penguins" dataset
data("penguins", package = "palmerpenguins")
```

#### Write a short description of the `penguins` dataset:
```{r}
## show the dataset
penguins
## names of important variables
names(penguins)
## the size of dataset
dim(penguins)
nrow(penguins)
ncol(penguins)
## the mean of flipper length
mean(penguins$flipper_length_mm, na.rm = T)
```

#### Make a scatterplot of `flipper_length_mm` vs `bill_length_mm` 
```{r warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) +
  geom_point(aes(color = species)) +
  ggtitle("Bill Length vs Flipper Length")
```

#### Save the plot
```{r message = FALSE, warning = FALSE, eval = FALSE}
ggsave("hw1_scatterplot.pdf")
```



